Avancement du stage

### 2025-05-12 presentation.qmd
Mise à jour présentation sans GHA [skip ci]

# Bornes des années utilisées pour la standardisation
min_year, max_year = config["years"]["min"], config["years"]["max"]
std_year = (max_year - min_year) / 2  # σₜ = (max - min) / 2

>>>>

# Bornes des années utilisées pour la standardisation
min_year, max_year = config["years"]["min"], config["years"]["max"]
std_year = max_year - min_year
